The Dark \LaTeX{} \\ \large An Example of the dndbook Class

### 2020-01-18 example.tex

\section{Items and Spells}
The module also includes the functions |\DndItemHeader| and |\DndSpellHeader| to aid in the proper typesetting of items (including magic items and traps) and spells.

>>>>

\section{Special Sections}
The module also includes functions to aid in the proper typesetting of multi-line section headers: |\DndFeatHeader| for feats, |\DndItemHeader| magic items and traps, and |\DndSpellHeader| for spells.

\DndFeatHeader{Typesetting Savant}[Prerequisite: \LaTeX{} distribution]
You have acquired a package which aids in typesetting source material for one of your favorite games. You have advantage on Intelligence checks to typeset new content. On a failed check, you can ask questions online at the package's website.
